Untitled

### 2017-07-21 PaperCode.Rmd
Big Fix on property types
I hadn't put in the property types value in the section that creates the new BootStrapRES data, this mean that property types were ignored.

#Investigating Ceredigion

Ceredigion has cheaper LUps even though it has areas with high LUP. When investigating I changed the classes to take account of the different pricing levels in the LAD. This made no difference. However re-running the bootstrapping including only A type purchases in the LAD gave the expected result of high LUP prices. What appeared to be happening was a lot of property was being transferred in unsual ways.

CeredPrice <- prices %>% 
  filter( grepl("E09000001", Admin_district_code)) %>%
  select(Admin_ward_code, lsoa11cd, Price =X2, X15) %>%
  #filter(X15 == "A") %>%
  mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
                     labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
                     right = F),
         Price = as.numeric(Price))

CeredPrice2 <- CeredPrice %>%
  group_by(lsoa11cd, class) %>%
  summarise(Admin_ward_code = first(Admin_ward_code),
            LSOAcounts = n())

CeredPrice2 <- CeredPrice2  %>%
  group_by(Admin_ward_code, class) %>%
  summarise(counts = n()) %>%
  group_by(class) %>%
  mutate(ClassPercent = counts/sum(counts)) %>%
  ungroup %>% group_by(Admin_ward_code) %>%
  mutate(WardPercent = counts/sum(counts))%>%
  left_join(CeredPrice2,. ,by=c("Admin_ward_code", "class")) %>%
  rename(LSOA_CODE = lsoa11cd)

RBKCPrice <- prices %>% 
  filter( grepl("E09000020", Admin_district_code)) %>%
    select(Admin_ward_code, lsoa11cd, Price =X2, X15) %>%
  #filter(X15 == "A") %>%
  mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
                     labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
                     right = F),
         Price = as.numeric(Price))

RBKCPrice2 <- RBKCPrice %>%
  group_by(lsoa11cd, class) %>%
  summarise(Admin_ward_code = first(Admin_ward_code),
            LSOAcounts = n())

RBKCPrice2 <- RBKCPrice  %>%
  group_by(Admin_ward_code, class) %>%
  summarise(counts = n()) %>%
  group_by(class) %>%
  mutate(ClassPercent = counts/sum(counts)) %>%
  ungroup %>% group_by(Admin_ward_code) %>%
  mutate(WardPercent = counts/sum(counts))%>%
  left_join(RBKCPrice2,. ,by=c("Admin_ward_code", "class")) %>%
  rename(LSOA_CODE = lsoa11cd)

RBKCtot <- RBKCPrice2 %>%
  group_by(class) %>%
  summarise(counts = sum(counts))

summary(CeredPrice$Price)
summary(RBKCPrice$Price)

# CeredBootAnorm <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, type = "A" )
# CeredBootAB <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, c(0, 60, 120, 200, 500, Inf)*10^3 )
# 
# CeredBootA <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, c(0, 60, 120, 200, 500, Inf)*10^3, type = "A" )

ValueTtest(CeredBootAB)
ValueTtest(CeredBootA)
ValueTtest(CeredBootAnorm)

BootStrapRES$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

BootStrapRESA$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

BootStrapRESB$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

RBKCPrice %>% group_by(X15) %>%
  summarise(mean = mean(Price))

CeredPrice %>% group_by(X15) %>%
  summarise(mean = mean(Price))

 RBKCPrice2 %>%
   filter(class == "Prime") %>%
   PlotMap(.,AG,  "ClassPercent")

  CeredPrice2 %>%
   filter(class == "Mid") %>%
   PlotMap(.,filter(AG, LAD11CD=="W06000008"), variable = "ClassPercent", filtermap = FALSE)

@@

@@

test <- BootStrapRES$Ceredigion
#look at specific data
BootStrapRESA$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

BootStrapRES$ChelseaLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

BootStrapRESA$ChelseaLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

BootStrapRESB$ChelseaLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

BootStrapRES$CoLLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

BootStrapRESA$CoLLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

BootStrapRESB$CoLLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

@@

#test CoL after adding in filtering for other LADs
testCol <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000)
testColA <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000, "A")
testColB <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000, "B")

testColA %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

@@

testB <- ChelseaLONDATA %>% SubsetPrice("B") %>% left_join(HouseMatch)
testA <- ChelseaLONDATA %>% SubsetPrice("A") %>% left_join(HouseMatch)

testB <- ChelseaLONDATA %>% SubsetPrice("B") %>% left_join(HouseMatch)
testA <- ChelseaLONDATA %>% SubsetPrice("A") %>% left_join(HouseMatch)

test <- CoLLONDATA %>% SubsetPrice("A")

>>>>

@@

#Excluding Other
Combine1ExO <- BootResSummaryData(BootStrapRESExO) %>% mutate(LAD11CD = CurrentLADS)

Combine2ExO <- BootResSummaryData(BootStrapRESExOA) %>% mutate(LAD11CD = CurrentLADS)

Combine3ExO <- BootResSummaryData(BootStrapRESExOB) %>% mutate(LAD11CD = CurrentLADS)

@@

#Explore results

BootStrapRES$CoLLON %>% PlotClassDiff()
BootStrapRESExO$CoLLON %>% PlotClassDiff()
BootStrapRESA$CoLLON %>% PlotClassDiff()
BootStrapRESB$CoLLON %>% PlotClassDiff()

@@

#test CoL after adding in filtering for other LADs
testCol <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000, PropertyTypes = c("D", "S", "T", "F"))

testColA <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000, "A", PropertyTypes = c("D", "S", "T", "F"))
testColB <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000, "B", PropertyTypes = c("D", "S", "T", "F"))

all_equal(Boottest$CoLLON, testCol)

all_equal(Boottest$CoLLON, BootStrapRES$CoLLON)

testCol %>% PlotClassDiff()

@@
